---
title: dform
description: Downloads and manages simple data processing tasks for SEC Form D data.
author: Matt Rogers
date: '2026-05-08'
categories:
  - R Package
  - Economic Indicators
tags:
  - SEC Form D
  - Securities
  - Business Formation
  - County-Level
  - Caching
  - Data Processing
package:
  name: dform
  githubUrl: https://github.com/ruralinnovation/dform
  installCommand: devtools::install_github("ruralinnovation/dform")
  status: development
  version: 0.0.1
  maintainer: Matt Rogers
  featured: false
usesDatasets:
  - sec-form-d
usesResources: []
execute:
  echo: true
  warning: false
  message: false
editor:
  markdown:
    wrap: 72
---

## Overview

dform provides a programmatic interface to SEC Form D data through an R6 class. Form D is the notice of offering filed by companies with the SEC under Regulation D, containing information about securities offerings including issuer details, offering terms, and recipient information. This package automates downloading quarterly datasets from the SEC's EDGAR system, manages local caching to reduce redundant downloads, and handles de-duplication and aggregation of the various data tables.

::: callout-note
## Why Use This Package

- **SEC EDGAR Integration** - Downloads directly from SEC EDGAR structured data API for Form D filings
- **Local Caching** - Caches downloaded quarterly datasets locally to avoid redundant downloads
- **De-duplication** - Removes duplicate offerings using previous accession numbers
- **Multi-table Processing** - Handles six related data tables: submissions, issuers, offerings, recipients, related persons, and signatures
- **Data Aggregation** - Aggregates multiple rows per accession number using configurable separators
- **Method Chaining** - Public methods return invisible(self) for fluent interface
:::

## Installation

```{r}
#| eval: false

devtools::install_github("ruralinnovation/dform")
```

## Quick Start

```{r}
#| eval: false

dfm <- dForm$new()

# Load Form D data for 2020, cache results, remove duplicates.
# `contact` is required — see "SEC access requirement" below.
dfm$load_data(
  2020, quarter = c(1:4), remove_duplicates = TRUE, use_cache = TRUE,
  contact = "Your Organization you@example.org"
)

# Access the loaded data
head(dfm$submissions)
head(dfm$issuers)
head(dfm$offerings)

# Aggregate related data by accession number
dfm$aggregate_data(sep = "; ")

# Combine multiple tables
combined <- dfm$combine_data(tables_to_combine = c("submissions", "offerings", "issuers"))
```

::: callout-important
## SEC access requirement

SEC's access policy requires a User-Agent that declares who you are with a
contact email. dForm's bundled downloader (`R/download_file.R`) sends a
hardcoded Firefox User-Agent plus a `Referer: broadbandmap.fcc.gov` header — an
FCC copy-paste that's both wrong for SEC and bot-looking — so SEC blocks it,
returning a 403 "Request Rate Threshold Exceeded" page instead of the data.

The fix is to make the Form D download send a SEC-compliant User-Agent.
`load_data()` takes a **required** `contact` argument (no default) — your
organization plus a contact email — threaded through to the downloader and
appended to the User-Agent so SEC serves the data. Omitting it (or passing a
blank/invalid value) raises a clear error up front rather than failing later
with a confusing "no data" message.
:::

## Core Functions

| Function | Description |
|----------|-------------|
| `dForm()` | R6 class for downloading, caching, and processing SEC Form D data |

## Data Sources

| Dataset | Role |
|---------|------|
| [SEC Form D](/datasets/sec-form-d/) | Primary |

## Use Cases at CORI

This package is used in:

- Analyzing private securities offerings by geography and industry
- Researching entrepreneurship and business formation patterns
- Studying capital formation trends across counties
- Building county-level datasets on securities activity

::: callout-tip
## Optimization Tips

Use use_cache = TRUE (default) to avoid re-downloading data. For large years or multiple quarters, consider loading data in batches to manage memory usage.
:::

::: callout-warning
## Known Limitations

Package version 0.0.1 is in development. Codebook generation is currently disabled (commented out) and may be added in future versions.
:::

## Documentation

- [GitHub Repository](https://github.com/ruralinnovation/dform)
- [Full README](https://github.com/ruralinnovation/dform/blob/main/README.md)
- [Function Documentation](https://github.com/ruralinnovation/dform/tree/main/man)

